Learning and comparing functional connectomes between populations

### 2012-12-30 paper.tex
intro done!

% Give a layout of the paper

>>>>

% Give a layout of the paper
The paper is organized has follows. First we discuss estimation of
functional connectomes. This part, akin to a first-level analysis in
standard activation mapping methodology, is not in itself a group-level
operation, but it is a critical step for inter-subject comparison.
In a following section, we discuss several strategies for comparing
connectomes across subjects. Finally we discuss the links between the
representation of brain connectivity as graphs of functional connectivity
and more complex models, such as effective-connectivity models.
